---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hext

<!-- badges: start -->
[![Project Status: Concept – Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
<!-- badges: end -->

> [!NOTE]
> Very much a concept that I may or may not develop in future.

```{r}
#| label: hext-logo-top
#| echo: false
hext::make_hext()
```

## About

Hex stickers... but text.

[Bye, hex stickers](https://yihui.org/en/2026/02/bye-stickers/).
Welcome back Yihui.

Inspired by artistry in [Yihui's {litedown}](https://github.com/yihui/litedown) and then [Charlie's {secretbase}](https://github.com/shikokuchuo/secretbase/).

## Install

The package is a GitHub exclusive for now.

```r
install.packages("pak") # if not yet installed
pak::pak("matt-dray/hext")
```

You can add (`text_1`, etc) and align (`align_1`, etc) text on each of the hex's four lines.

To make this package's logo:

```{r}
#| label: hext-logo-example
# fmt: skip
hext::make_hext(
  line_2 = "⬡⬢", align_2 = "centre",
  line_3 = "hext", align_3 = "centre"
)
```

A more complex example:

```{r}
#| label: hext-align
# fmt: skip
hext::make_hext(
  " hello", "this ", "is", "_hext",
  "left", "right", "centre", "left"
)
```

Your kilometreage may vary with non-[ASCII characters](https://en.wikipedia.org/wiki/ASCII) like emojis.
Text is best.
Doesn't mean artistry is out of the question.

```{r}
#| label: hext-cat
hext::make_hext(
  r"{/\__/\}",
  "={ o x o}=",
  "l(  u u )",
  "_b___b"
)
```

## Sage advice

Keep it simple.

No, you didn't hear me.

_Simpler_.

## The Text-Stickers Standard

You may be aware of the [the Stickers Standard](https://sticker.how/#type-hexagon).
Too complex.

Canoncially, the flat-bottomed text-hex is:

* [2 spaces][8 underscores]
* [1 space][1 slash][8 spaces][1 backslash]
* [1 slash][10 spaces][1 backslash]
* [1 backslash][10 spaces][1 slash]
* [1 space][1 backslash][8 underscores][1 slash]

That's four possible lines that can contain text.

Trailing spaces to 'square-off' are acceptable but unnecessary.

## Gallery

> [!NOTE]
> Please [raise a PR](https://github.com/matt-dray/hext/pulls) to add to this illustrious gallery.

\#000001: [{litedown}](https://github.com/yihui/litedown) by Yihui Xie

```
[Reproduction awaiting clearance]
```

\#000002: [{secretbase}](https://github.com/shikokuchuo/secretbase/) by Charlie Gao

```
[Reproduction awaiting clearance]
```

\#000003: [{hext}](https://github.com/matt-dray/hext/) by Matt Dray

```{r}
#| label: hext-logo-gallery
#| echo: false
hext::make_hext()
```

## Overcomplicated file-based hexes

If you're interested in jpegs or whatever, see:

* [{hexSticker}](https://github.com/GuangchuangYu/hexSticker) by Guangchang Yu
* [hexmake](https://github.com/ColinFay/hexmake) by Colin Fay
* [{bunny}](https://github.com/dmi3kno/bunny) by Dmytro Perelpolkin
* [{gex}](https://github.com/matt-dray/gex) by Matt Dray (disclaimer: that's my name)
